Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-11-04 paper/pool_model.tex
fix line numbers
fix notation of total bacteria

\setlength{\tabcolsep}{1.3pt}
\setlength{\columnsep}{0.4cm}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
% \usepackage[a4paper,inner=2cm,outer=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage{lineno}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{onimage}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{tikz}
%\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

\linenumbers

@@

\maketitle
%
% ================================================================================================
\section{Introduction}

@@

Note that the previously introduced model could be further simplified to a two pool or state model by omitting the pool $D$ and removing cells with rate $\beta$ directly from pool $L$.

@@

If yes, the three pool model would be advantageous, if not the two pool model is sufficient with the advantage of having one parameter less.\\

@@

It is interesting to see what type of equations result for the total bacterial population $N=L+G+D$:

@@

        \dot{G} &= \lambda L + \alpha G\left(1-\frac{N}{N_t}\right)\\
        \dot{N} &= \alpha G\left(1-\frac{N}{N_t}\right)

@@

with initial conditions $G(0)=0$ and $N(0)=N_0$.

>>>>

\setlength{\tabcolsep}{1.3pt}
\setlength{\columnsep}{0.4cm}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
% \usepackage[a4paper,inner=2cm,outer=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage[switch]{lineno}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{onimage}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{tikz}
%\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

@@

\maketitle
\linenumbers
%
% ================================================================================================
\section{Introduction}

@@

Note that the previously introduced model could be further simplified to a two pool or state model by omitting the pool $D$ and removing cells directly from pools $L$ and $G$.

@@

If yes, the three pool model would be advantageous, if not the two pool model is sufficient with the benefit of having one parameter less.\\

@@

It is interesting to see what type of equations result for the total bacterial population $\mathcal{N}=L+G+D$:

@@

        \dot{G} &= \lambda L + \alpha G\left(1-\frac{\mathcal{N}}{N_t}\right)\\
        \dot{\mathcal{N}} &= \alpha G\left(1-\frac{\mathcal{N}}{N_t}\right)

@@

with initial conditions $G(0)=0$ and $\mathcal{N}(0)=N_0$.
